\vskip-0.6in \Large Political Uncertainty

### 2015-04-23 GS-extension.tex
add solution to base model; start separate page for calculations
add math that supports base model solution

			The two symmetric conditions would be:
			\begin{multline}
					\Phi\left(- \alpha + b(0) \right)+  \Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right) 
					- 2 \Phi\left(- \alpha + b(0) \right)\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right) \\ = \frac{\sqrt{2\pi}}{W_B \: e^{- \frac{\left(\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)\right)^2}{2}} }
				\end{multline}
			\begin{multline}
					\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)+  \Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) 
					- 2 \Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2})\right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)\\ = \frac{\sqrt{2\pi}}{W_B \: e^{- \frac{\left( - \alpha + b\left(0\right)\right)^2}{2}} }
				\end{multline}
		\end{itemize}
	\item Some notes
		\begin{itemize}
			\item If we divide through by 2, the left side is the average minus the product
			\item If that is set equal to zero, the only solutions (for just one equation) are at (0,0) and (1,1). The right hand side modifies that.
			\item Need to check SOC at some point
			\item Remember, I'm ignoring the constraints on WTP and non-negativity of bribes
			\item First I'm going to try to get closed form answer / intuition by substituting logistic for normal CDF/PDF
		\end{itemize}
	\item Substituting logistic for normal in Equation~\ref{eq:firstfoc}
		\begin{equation}
					\frac{e^{- \alpha + b(0)}}{1+e^{- \alpha + b(0)}} + \frac{e^{\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)}}{1+e^{\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) }}
					- 2\frac{e^{- \alpha + b(0)}}{1+e^{- \alpha + b(0)}}  \frac{e^{\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) }}{1+e^{\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) }} = \frac{\left(1+e^{\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)}\right)^2}{W_B \: e^{\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)} }
				\end{equation}
\end{itemize}

@@

>>>>

			The two symmetric conditions would be:
			\begin{multline}
					\Phi\left(- \alpha + b(0) \right)+  \Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right) 
					- 2 \Phi\left(- \alpha + b(0) \right)\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right) \\ = \frac{\sqrt{2\pi}}{W_B \: e^{- \frac{\left(\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)\right)^2}{2}} }
				\end{multline}
			\begin{multline}
					\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)+  \Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) 
					- 2 \Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2})\right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)\\ = \frac{\sqrt{2\pi}}{W_B \: e^{- \frac{\left( - \alpha + b\left(0\right)\right)^2}{2}} }
				\end{multline}
		\end{itemize}
	\item Some notes
		\begin{itemize}
			\item If we divide through by 2, the left side is the average minus the product
			\item If that is set equal to zero, the only solutions (for just one equation) are at (0,0) and (1,1). The right hand side modifies that.
			\item Need to check SOC at some point
			\item Remember, I'm ignoring the constraints on WTP and non-negativity of bribes
			\item First I'm going to try to get closed form answer / intuition by substituting logistic for normal CDF/PDF
		\end{itemize}
	\item Substituting logistic for normal in Equation~\ref{eq:firstfoc}
		\begin{equation}
					\frac{e^{- \alpha + b(0)}}{1+e^{- \alpha + b(0)}} + \frac{e^{\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)}}{1+e^{\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) }}
					- 2\frac{e^{- \alpha + b(0)}}{1+e^{- \alpha + b(0)}}  \frac{e^{\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) }}{1+e^{\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) }} = \frac{\left(1+e^{-\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)}\right)^2}{W_B \: e^{-\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)} }
					\label{eq:logistic}
				\end{equation}
		\begin{itemize}
			\item A LOT of math (I will put it somewhere else) leads to three equations:
				\[
				  \left[ - \alpha + b(0) \right] = \left[ \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) \right] + \left[ -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right) \right]
				\]
				\[
				   \left[ \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) \right] =\left[ - \alpha + b(0) \right]+ \left[ -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right) \right]
				\]
				\[
				   \left[ -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right) \right] = \left[ \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) \right] +\left[ - \alpha + b(0) \right]
				\]
			\item A little more math implies that all three quantities in brackets must equal zero.
		\end{itemize}
\end{itemize}

@@

\newpage
The math that follows from Equation \ref{eq:logistic}:
\begin{itemize}
	\item Let
		\begin{enumerate}
			\item $ X - \alpha + b(0)$ 
			\item $Y = \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)$
			\item $Z = -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)$
		\end{enumerate}
	\item Then Equation \ref{eq:logistic} is equivalent to:
		\begin{equation}
			\frac{e^{X}}{1+e^{X}} + \frac{e^{Y}}{1+e^{Y }} - 2\frac{e^{X}}{1+e^{X}}  \frac{e^{Y }}{1+e^{Y }} = \frac{\left(1+e^{Z}\right)^2}{W_B \: e^{Z} }
					\label{eq:logistic2}
		\end{equation}
		\[
			\frac{e^{X} + 2e^{X+Y} + e^{Y}}{\left(1+e^{X}\right)\left(1+e^{Y }\right)} - 2\frac{e^{X+Y}}{\left(1+e^{X}\right)\left(1+e^{Y }\right)} = \frac{\left(1+e^{Z}\right)^2}{W_B \: e^{Z} }
		\]
		\[
			\frac{e^{X} + e^{Y}}{\left(1+e^{X}\right)\left(1+e^{Y }\right)} = \frac{\left(1+e^{Z}\right)^2}{W_B \: e^{Z} }
		\]
		\begin{equation}
			\frac{e^{X} + e^{Y}}{\left(1+e^{X}\right)\left(1+e^{Y }\right)} \frac{e^{Z}}{\left(1+e^{Z}\right)^2}= \frac{1}{W_B}
		\end{equation}
		Likewise, we have
		\begin{equation}
			\frac{e^{X} + e^{Z}}{\left(1+e^{X}\right)\left(1+e^{Z}\right)} \frac{e^{Y}}{\left(1+e^{Y}\right)^2}= \frac{1}{W_B}
		\end{equation}
		Setting the left-hand size of these two equations equal to each other,
		\[
		  \frac{e^{X} + e^{Y}}{\left(1+e^{X}\right)\left(1+e^{Y }\right)} \frac{e^{Z}}{\left(1+e^{Z}\right)^2}= \frac{e^{X} + e^{Z}}{\left(1+e^{X}\right)\left(1+e^{Z}\right)} \frac{e^{Y}}{\left(1+e^{Y}\right)^2}
		\]
		\[
		  \frac{e^{X+Z} + e^{Y+Z}}{1+e^{Z}}= \frac{e^{X+Y} + e^{Y+Z}}{1+e^{Y}}
		\]
		\[
		  e^{X+Z} + e^{Y+Z} + e^{X+Y+Z} +e^{2Y+Z}= e^{X+Y} + e^{Y+Z} + e^{X+Y+Z} +e^{Y+2Z}
		\]
		\[
		  e^{X+Z} +e^{2Y+Z}= e^{X+Y} +e^{Y+2Z}
		\]
		\[
		  e^{X}\left(e^{Z} - e^{Y} \right) = e^{Y+Z}\left(e^{Z} - e^{Y} \right)
		\]
		\[
		  e^{X} = e^{Y+Z}
		\]
		\[
		  X = Y+Z
		\]
		By symmetry, we also have
		\[
		  Y = X + Z
		\]
		\[
		  Z = X + Y
		\]
\end{itemize}
